---
title: "Data analysis pilots"
author: "Nathanael Larigaldie"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    toc: yes
    latex_engine: lualatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(afex)
library(emmeans)
library(gridExtra)
library(sjPlot)
library(sjmisc) 
library(effects)
library(sjstats)
library(simr)
```

## Dataset loading

```{r}
datasets       <- list.files(file.path("final_data"), pattern="*.csv", full.names = TRUE)
datasets       <- lapply(datasets, read_csv, show_col_types = FALSE)

d <- datasets[[1]]
for (i in seq(from=2, to=length(datasets)))
{
  d <- rbind(d, datasets[[i]])
}
```

## Dataset preparation

```{r}
d <- d %>% mutate(Subject=rep(seq_len(length(datasets)), each=100))
```

Then we remove fixation times <=1500ms, scale the Agreement feature and take its square, and log-transform Fixation.Time

```{r}
d_final <- d %>% filter(Fixation.Time > 1500) %>%
  mutate(Fixation.Time.Log = log(Fixation.Time),
         Agreement.Scaled = (Agreement-mean(Agreement))/sd(Agreement),
         Squared.Agreement.Scaled=Agreement.Scaled^2,
         Index=as.factor(Index), Subject=as.factor(Subject))
```

## Variables plot (violin & boxplot + density)

```{r}

violin_fixation <- ggplot(d_final, aes(x="Fixation time", y=Fixation.Time.Log)) +
  ylab("Fixation Time (log)") + theme_minimal() +
  theme(legend.position = "none") +
  geom_violin(width=1.2) + geom_boxplot(width=0.1, alpha=0.2)


violin_agreement <- ggplot(d_final, aes(x="Agreement", y=Agreement.Scaled)) +
  ylab("Agreement (scaled)") + theme_minimal() +
  theme(legend.position = "none") +
  geom_violin(width=1.2) + geom_boxplot(width=0.1, alpha=0.2)

density_fixation <- ggplot(d_final, aes(x=Fixation.Time.Log)) + geom_density()
  
density_agreement <- ggplot(d_final, aes(x=Agreement.Scaled)) + geom_density()

grid.arrange(violin_fixation, violin_agreement, density_fixation,
             density_agreement, nrow=2)

```

## Statistical model

```{r}
res_mixed <- lmer(Fixation.Time.Log ~ Agreement.Scaled +
                    Squared.Agreement.Scaled +
                    (1 | Index) +
                    (Agreement.Scaled + Squared.Agreement.Scaled | Subject),
                  data=d_final, control = lmerControl(optimizer ="bobyqa"))

summary(res_mixed)
plot_model(res_mixed,
           axis.labels=c("Agreement (Quadratic)", "Agreement"),
           show.values=TRUE, show.p=TRUE,
           title="Quadratic effect of Agreement on Fixation Times")

quad_function <- function(x, alpha, beta1, beta2)
{
  return(alpha + beta1*x + beta2*x^2)
}
```

### Random effect plot

```{r}
ggplot() +
  geom_point(data=d_final, aes(Agreement.Scaled, Fixation.Time.Log)) +
  geom_function(fun=quad_function,
                args=list(alpha=summary(res_mixed)[["coefficients"]][1],
                                        beta1=summary(res_mixed)[["coefficients"]][2],
                                        beta2=summary(res_mixed)[["coefficients"]][3]),
                color="blue",
                linewidth=1.5)

```

### Residuals analysis

```{r}
qqnorm(residuals(res_mixed))
qqline(residuals(res_mixed))
hist(residuals(res_mixed))
ks.test(x=residuals(res_mixed), y='pnorm')
```

